Waking Up a Sleeping Rabbit:\\ On Natural-Language Sentence Generation with FF

### 2010-03-01 trunk/Papers/crisp-ff-10/main.tex
minor..

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Alexander Koller, Joerg Hoffmann)
/Title (Waking up a sleeping rabbit: On Natural-Language Sentence Generation with FF)
/Keywords (AAAI, artificial intelligence)
/DOCINFO pdfmark}

@@

\begin{document}
\title{Waking up a sleeping rabbit:\\ On Natural-Language Sentence Generation with FF}

>>>>

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Alexander Koller, Joerg Hoffmann)
/Title (Waking Up a Sleeping Rabbit: On Natural-Language Sentence Generation with FF)
/Keywords (AAAI, artificial intelligence)
/DOCINFO pdfmark}

@@

\begin{document}
\title{Waking Up a Sleeping Rabbit:\\ On Natural-Language Sentence Generation with FF}
